---
title: "Assessment 1.1"
author: "Name"
date: "10/22/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(knitr)
library(markdown)
library(dplyr)
library(ggplot2)
library(skimr)
library(ggpubr)
theme_set(theme_pubr())
```


## Part 1


# RMarkdown editing
# **R Markdown is a file format for making dynamic documents with R**
# **R Markdown document is written in markdown and contains chunks of embedded R code**


```{r}
fastfood<-fread('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')
kable(head(fastfood[, 2:6],10), "simple")
filter(fastfood, calories> 1000)
dont_eat_this<-filter(fastfood, total_fat>40, total_carb>80)
filter(fastfood, restaurant=='Mcdonalds')
```


## Part 2


```{r}
skim(fastfood)
fastfood %>%
     group_by(restaurant) %>%
     summarise(Count = n()) 
fastfood %>%
     group_by(restaurant) %>%
     summarise(average_calories= mean(calories))
fastfood %>%
     group_by(restaurant) %>%
     summarise(total_fat= sum(total_fat))%>%
ggplot(aes(x = restaurant, y = total_fat, fill = restaurant)) +
    geom_bar(stat = "identity") +
    theme_classic() +
    labs(
        x = "Restaurants",
        y = "Total Fat",
        title = paste(
            "Total Fat per Restaurants"
        )
    )

fastfood %>%
     group_by(restaurant) %>%
     summarise(max_total_fat= max(total_fat))
mcdata<-filter(fastfood, restaurant=='Mcdonalds')
mcdata %>%
ggplot(aes(x = protein, y =sugar)) +
    geom_point(stat = "identity") +
    theme_classic() +
    labs(
        x = "Protein",
        y = "Sugar",
        title = paste(
            "Sugar versus Protein"
        )
    )
```


Bar charts are effective data visualization that display well summed data. Therefore, i have used bar charts to represent the total fat for each restaurant. From the chart, an easy comparison for the restaurants can be made.

## Part 3

```{r}
fastfood <- mutate_at(fastfood, vars(restaurant), as.factor)
str(fastfood)
fastfood$calories_type<-cut_number(fastfood$calories, 3)
fastfood$calories_type<-factor(fastfood$calories_type,labels=c("low", "med", "high"))
fastfood[order(fastfood$calories_type),]
ggplot(fastfood) + geom_bar(aes(x = calories_type))+
  facet_wrap(~restaurant) + 
  fill_palette("jco")
fastfood$trans_fat_percent<-(fastfood$trans_fat/fastfood$total_fat)*100
ggplot(fastfood, aes(x=restaurant, y=trans_fat, fill=restaurant)) +
  geom_bar(stat="identity")+theme_minimal()
fastfood %>%
     group_by(restaurant) %>%
     summarise(meanfat= mean(total_fat))
ggplot(fastfood, aes(x=restaurant, y=total_fat, fill=restaurant)) +
  geom_bar(stat="identity")+theme_minimal()
```










